Clustering, profiling and plots

### 2024-06-16 data/01-census-and-traveltimes.qmd
Incorporated Lea and Lucia's comments

@@

>>>>

```{r}
load( file="HAM_census_21.rda")
```

@@

## Transit travel times

Calculate **Transit** travel times from centroids of parcels (from_ids) to destination points (to_ids). 30 min max travel time.

```{r Transit travel time 1}
# set up batching according to how many origin rows to process at one time
chunksize = 50 
num_chunks = ceiling(nrow(orig_1)/chunksize)

for (i in 1:num_chunks){
  Orig_chunk <- get_chunk(origins_chunks, i)
  ttm_chunk <- travel_time_matrix(r5r_core = r5_HAM,
                          origins = Orig_chunk,
                          destinations = dest,
                          mode = c("TRANSIT"),
                          departure_datetime = as.POSIXct(strptime("08-06-2023 08:00:00", # 12 GMT is 8am in Toronto (EDT)
                                 format = "%d-%m-%Y %H:%M:%S")),
                          max_trip_duration = 30)

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "parcel-ttm/processing/output_ttm",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}
end.time <- Sys.time()
print(paste0("OD matrix calculation took ", round(difftime(end.time, start.time, units = "mins"), digits = 2), " minutes..."))
#"OD matrix calculation took 6.78 minutes..."
ttm_care_TRANSIT_parcel1 <- as.data.frame(output_df)

save("ttm_care_TRANSIT_parcel1", file = "parcel-ttm/ttm_care_TRANSIT_parcel1.rda")
rm("ttm_care_TRANSIT_parcel1")
```

```{r TRANSIT travel time 2}
# set up batching according to how many origin rows to process at one time
chunksize = 50 
num_chunks = ceiling(nrow(orig_2)/chunksize)

for (i in 1:num_chunks){
  Orig_chunk <- get_chunk(origins_chunks, i)
  ttm_chunk <- travel_time_matrix(r5r_core = r5_HAM,
                          origins = Orig_chunk,
                          destinations = dest,
                          mode = c("TRANSIT"),
                          departure_datetime = as.POSIXct(strptime("08-06-2023 08:00:00", # 12 GMT is 8am in Toronto (EDT)
                                 format = "%d-%m-%Y %H:%M:%S")),
                          max_trip_duration = 30)

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "parcel-ttm/processing/output_ttm",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}
end.time <- Sys.time()
print(paste0("OD matrix calculation took ", round(difftime(end.time, start.time, units = "mins"), digits = 2), " minutes..."))
#"OD matrix calculation took 5.35 minutes..."
ttm_care_TRANSIT_parcel2 <- as.data.frame(output_df)

save("ttm_care_TRANSIT_parcel2", file = "parcel-ttm/ttm_care_TRANSIT_parcel2.rda")
rm("ttm_care_TRANSIT_parcel2")
```

```{r TRANSIT travel time 3}
# set up batching according to how many origin rows to process at one time
chunksize = 50 
num_chunks = ceiling(nrow(orig_3)/chunksize)

for (i in 1:num_chunks){
  Orig_chunk <- get_chunk(origins_chunks, i)
  ttm_chunk <- travel_time_matrix(r5r_core = r5_HAM,
                          origins = Orig_chunk,
                          destinations = dest,
                          mode = c("TRANSIT"),
                          departure_datetime = as.POSIXct(strptime("08-06-2023 08:00:00", # 12 GMT is 8am in Toronto (EDT)
                                 format = "%d-%m-%Y %H:%M:%S")),
                          max_trip_duration = 30)

ttm_care_TRANSIT_parcel3 <- as.data.frame(output_df)

save("ttm_care_TRANSIT_parcel3", file = "parcel-ttm/ttm_care_TRANSIT_parcel3.rda")
rm("ttm_care_TRANSIT_parcel3")
```

```{r TRANSIT travel time 4}
# set up batching according to how many origin rows to process at one time
chunksize = 50 
num_chunks = ceiling(nrow(orig_4)/chunksize)

for (i in 1:num_chunks){
  Orig_chunk <- get_chunk(origins_chunks, i)
  ttm_chunk <- travel_time_matrix(r5r_core = r5_HAM,
                          origins = Orig_chunk,
                          destinations = dest,
                          mode = c("TRANSIT"),
                          departure_datetime = as.POSIXct(strptime("08-06-2023 08:00:00", # 12 GMT is 8am in Toronto (EDT)
                                 format = "%d-%m-%Y %H:%M:%S")),
                          max_trip_duration = 30)

ttm_care_TRANSIT_parcel4 <- as.data.frame(output_df)

save("ttm_care_TRANSIT_parcel4", file = "parcel-ttm/ttm_care_TRANSIT_parcel4.rda")
rm("ttm_care_TRANSIT_parcel4")
```

### 2024-06-16 data/03-clustering-and-profiling.qmd
Incorporated Lea and Lucia's comments

SClabel_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(df_DA) +
  tm_polygons("max_label",
              border.alpha = 0.2,
              palette = c("darkolivegreen","red", "dodgerblue", "darkorchid","darkgreen"),
              labels = (c("Very caring - very complete (SC2)","Caring - Complete (SC1)",
              "Somewhat caring - complete (SC4)","Somewhat caring - somewhat complete (SC5)", 
              "Somewhat caring - somewhat complete (SC3)")),
              title = "Prevelant supercluster") +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("left", "top"), size=1.0)+
  tm_layout(legend.bg.color = "white", legend.bg.alpha = 0.4,
            bg.color = "grey",
            legend.position = c("right","top"))
SClabel_copp_plot
SCLab_and_total_copp_plot <- tmap_arrange(SClabel_copp_plot, total_copp_plot, nrow=2)

>>>>

SClabel_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(df_DA) +
  tm_polygons("max_label",
              border.alpha = 0.2,
              palette = c("#44ce1b","#bbdb44", "#f7e379", "#f2a134","#e51f1f"),
              labels = (c("Very caring - very complete (SC2)","Caring - Complete (SC1)",
              "Somewhat caring - complete (SC4)","Somewhat caring - somewhat complete (SC5)", 
              "Somewhat caring - somewhat complete (SC3)")),
              title = "Prevelant supercluster") +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("left", "top"), size=1.0)+
  tm_layout(legend.bg.color = "white", legend.bg.alpha = 0.4,
            bg.color = "grey",
            legend.position = c("right","top"))
SClabel_copp_plot
SCLab_and_total_copp_plot <- tmap_arrange(SClabel_copp_plot, total_copp_plot, nrow=2)
